\speculake: Hiding Malware in Speculative Execution

### 2018-12-10 paper/figures.tex
fix table formatting
filled table

\newcommand{\processorTable}{
\begin{table}
    \centering
    \resizebox{\linewidth}{!}{\begin{tabularx}{\linewidth}{l X X| Y Y Y}
        Processor & Year\newline
        released & Micro\newline
        arch & Nested\newline 
        Spec? & Num\newline
        indirect jumps* & Max $\mu$~ops\newline
        (nop)\\
        \hline
        Intel Xeon CPU E3-1270 v6 & 2017 & Skylake & \checkmark & 28 & 220\\
        Intel Core i5-7200U       & 2016 & Skylake & \checkmark & 26 & 220\\
        Intel Xeon CPU E3-1276 v3 & 2014 & Haswell &            & ?  & ?  \\
        AMD EPYC 7251             & 2017 & Ryzen   &            & ?  & ?  \\
    \end{tabularx}}
    \caption{\textbf{Processor features}--- We analyzed the capability of
    \speculake on three Intel and one AMD processor. Both Skylake processors
    were capable of nested speculation (Section~\ref{sssec:nested-spec}) though
    the older Haswell processor and the AMD processor were not. We found that
    the Intel Xeon CPU E3-1270 v6 required 28 identical indirect jumps in the
    trigger and payload programs to reliably enter the speculative world at the
    desired address ($> 95\%$) while the Intel Core i5-7200U only required 26
    jumps.}
    \label{table:processors}
\end{table}
}

>>>>

\newcommand{\processorTable}{
\begin{table}
    \centering
    % \resizebox{\linewidth}{!}{\begin{tabularx}{\linewidth}{X X X| Y Y Y}
    \begin{tabularx}{\linewidth}{X b b| Y Y Y}
        \ \newline
        \ \newline
        Processor & \ \newline
        Year\newline
        released & \ \newline
        Micro\newline
        arch & \ \newline
        Nested\newline 
        Spec? & Num\newline
        indirect jumps* & Max $\mu$~ops\newline
        (nop)\\
        \hline
        Intel Xeon CPU E3-1270 v6 & 2017 & Skylake & \checkmark & 28 & 220\\
        Intel Core i5-7200U       & 2016 & Skylake & \checkmark & 26 & 220\\
        Intel Xeon CPU E3-1276 v3 & 2014 & Haswell &            & 26 & 178\\
        AMD EPYC 7251             & 2017 & Ryzen   &            & 4  & 178\\
        \\
    \end{tabularx}%}
    \caption{\textbf{Processor features}--- We analyzed the capability of
    \speculake on three Intel and one AMD processor. Both Skylake processors
    were capable of nested speculation (Section~\ref{sssec:nested-spec}) though
    the older Haswell processor and the AMD processor were not. We found that
    the Intel Xeon CPU E3-1270 v6 required 28 identical indirect jumps in the
    trigger and payload programs to reliably enter the speculative world at the
    desired address ($> 95\%$) while the Intel Core i5-7200U only required 26
    jumps.}
    \label{table:processors}
\end{table}
}
